\addcontentsline{toc}{section}{Acknowledgements}
\section*{Acknowledgements}
This project would not have been possible without the help of dozens of people, both during the process of the SIP and before it was even a thought.  While this is by no means an exhaustive list, there are a number of people who must be thanked by name for their help.  I of course have to start by thanking my advisor Dr. Eric Barth for taking me on as an advisee.  This project has morphed a lot since he agreed to advise me on it, but he has been fully supportive in letting the project evolve naturally.  His guidance and support through these changes has been crucial.  In helping plan my initial project for my SIP, I must also thank Professor Andrew Koehler for his similar willingness to advise a project somewhat outside of his comfort zone.

As I developed the technologies discussed in my SIP over the summer, I would not have been able to do so without the mentorship and guidance of my co-workers at Maestro.  A huge thanks goes out to John Pinkster, Ben Meden, and Tyler VanderMaas for teaching me so much about back-end development.  Additionally, I have to thank Baxter Banghart for not entertaining phone calls throughout the summer where I would excitedly plan and develop these crazy ideas about GraphQL, but also for helping push me to be a better over the last eight years we've collaborated together.

This paper itself would also not be possible without the help of many people.  Thanks to Dr. Alyce Brady for entertaining my questions throughout the SIP Seminar and offering her years of wisdom she's gained through advising CS SIPs.  Thanks to all of my fellow CS students who proofread my paper as it was in the process of being written.  Additionally, thanks to my sister Amanda Gibson, for proofreading the paper as it neared its final draft.

Finally, I have to thank those who helped me get to where I am today.  A huge thanks goes out to Dr. Kelly Schultz.  She was the teacher who inspired my passion for Computer Science at such a young age and lead me to the computer science department at Kalamazoo College.  It makes me happy to know she's still teaching and inspiring young students today.  My other CS educators at Kalamazoo College, Dr. Alyce Brady, Dr. Pam Cutter, and Dr. Gerry Howser, have also played a huge part in developing me a computer scientist.  Without their education, I would not have the skills or ambition to tackle this kind of project.   And of course, I must also thank my parents, Scott and Kristine Gibson.  They have been nothing but supportive throughout all my education, whether it was helping me dual enroll in classes to help fuel my passion for computer science, encouraging me to study music in many different contexts and venues, or supporting me throughout college. No aspect of this project would be possible without them.
\newpage